Bayesian inference of prehistoric population dynamics from multiple proxies: a case study from north of the Swiss Alps

### 2023-09-27 manuscript/paper_revision_1.Rmd
slight changes in the course of a course

      institute: [IBOT, IAMFAMU]

@@

@@

# Code availability
The computer code used to generate the Bayesian Population model is provided in full in the Supplementary Information, together with information about the program and version used. The R code and Data are available online at https://github.com/MartinHinz/bayesian.demographic.reconstruction.2022 and is archived at https://doi.org/10.5281/zenodo.6594498.

>>>>

      institute: [IBOT, IAMFAMU, IOA]

@@

  - IOA: Institute of Archaeology, University College London

@@

# Code availability
The code used to generate the Bayesian Population model is provided in full in the Supplementary Information, together with information about the program and version used. The R code and Data are available online at https://github.com/MartinHinz/bayesian.demographic.reconstruction.2022 and is archived at https://doi.org/10.5281/zenodo.6594498.
